### 2017-06-09 doc/manuscript.Rmd
Incomplete addition of co-author edits

**Research Design and Methods**:
We used longitudinal data (3 visits over 6 years) from the Prospective
Metabolism and Islet Cell Evaluation (PROMISE) cohort of adults (n=477) who were at-risk
for diabetes at baseline. Glucose and insulin from an OGTT were used to calculate the
Matsuda index (ISI), HOMA2-%S, the Insulinogenic Index over HOMA-IR (IGI/IR),
and the Insulin Secretion-Sensitivity Index-2 (ISSI-2). Gas chromatography
quantified TAGFA composition. Generalized estimating equations (GEE) adjusted for
confounders and partial least squares (PLS) were used for the analysis.

@@

Hypertriglyceridemia is an extensively studied and well described disorder in
the dysregulation of metabolic function and subsequent negative health outcomes [@Chehade2013a].
It is a strong risk factor for cardiovascular disease [@DAgostino2004a; @Verges2015a]
and is involved in other metabolic disorders and phenomenon such as non-alcoholic
fatty liver disease [@Kawano2013a], the metabolic syndrome [@Alberti2009], and
the hypertriglyceridemic waist [@Lemieux2000a].
Circulating triacylglceride (TAG) concentration is commonly measured during
routine clinical assessment using enzymatic methods.
However, clinically measured TAG is limited as it
represents the full fatty acid spectrum within the TAG fraction as a summary
measure. There is increasing appreciation for the importance of specific fatty 
acid composition profiles in different plasma fractions on various health
outcomes [@Forouhi2014a; @Ma2015a; @Johnston2016a], however there are relatively
few studies that have explored the impact of the fatty acid composition in the TAG fraction [@Rhee2011a; @Lankinen2015a].

The interaction between TAG and insulin sensitivity is complex and involves 
components of a feedback system [@Verges2015a]. Greater resistance to insulin in
both the liver and muscle may result in greater production of TAG and secretion
of lipoproteins that transport TAG [@Yu2012a]. Likewise, greater TAG may
contribute to metabolic dysfunction and lipotoxicity in various tissues, such as
the beta-cells, and thus continue the cycle [@Verges2015a]. Given the
complexity and temporal nature of the relationship, long term studies with
multiple data collection time points are paramount to better understanding the underlying
biology and subsequent risk.

While several studies have documented prospective associations of 
hypertriglyceridemia with incident type 2 diabetes 
[@Chien2008a; @DAgostino2004a; @Schulze2009a], only a limited number of longitudinal
studies [@Rhee2011a; @Lankinen2015a] have examined the relationship between
TAG and its composition on the pathophysiological factors underlying diabetes, 
particularly on beta-cell function. Our objective was to examine the 
longitudinal role of the specific composition of the serum TAG fraction on 
OGTT-derived measures of insulin sensitivity and beta-cell function compared to 
clinically measured TAG in a Canadian population at risk for diabetes.

@@

Recruitment for the baseline visit of the Prospective Metabolism and Islet Cell Evaluation (PROMISE) 
cohort took place between 2004-2006 in London and Toronto, 
Canada. Individuals were selected to participant if they met the eligibility 
criteria of having one or more risk factors for type 2 diabetes mellitus, 
including obesity, hypertension, family history of diabetes, and/or a history of
gestational diabetes or birth of a macrosomic infant. A total of 736 individuals
attended the baseline visit. Subsequent examinations occurred every three years,
with data from three examination visits available for the present analysis
(2004-2006, 2007-2009, and 2010-2013). The current study
used data on participants who did not have diabetes at baseline, who
returned for one or more of the follow-up examinations, and who had samples
available for fatty acid measurements (n=477; see the CONSORT diagram in 
`r cite_sf('consort')`). Metabolic characterization, anthropometric
measurements, and questionnaires on lifestyle and sociodemographics were
administered at each examination visit. Research ethics approval was obtained from
Mount Sinai Hospital and the University of Western Ontario, and all participants
provided written informed consent. Data collection methods were standardized
across the 2 centres and research nurses were centrally trained.

@@

After 8-12 hours of overnight fasting, participants completed a 75g oral glucose tolerance test (OGTT) at 
each examination visit, with blood samples taken at fasting, 30 min, and 2 hr 
post-glucose load. Samples were subsequently processed and frozen at -70°C.
Alanine aminotransferase (ALT) was measured using standard laboratory 
procedures. Cholesterol, HDL, and clinically-measured TAG 
were measured using Roche Modular's enzymatic colorimetric tests (Mississauga, 
ON). Both insulin and glucose were
measured from OGTT blood samples at fasting, 30 minute,
and 2 hour time points. Specific insulin was measured with the Elecsys 1010 
(Roche Diagnostics, Basel, Switzerland) immunoassay analyzer and 
electrochemiluminescence immunoassay, which shows 0.05% cross-reactivity to 
intact human pro-insulin and the Des 31,32 circulating split form (Linco Res. 
Inc) and has a coefficient of variation (CV) of 9.3%. Glucose was determined 
using an enzymatic hexokinase (Roche Modular, Roche Diagnostics) with a 
detection range of 0.11 to 41.6 mmol/L and an inter-assay CV of <1.1% and an
intra-assay CV of < 1.9%.  All assays were performed at the Banting and Best
Diabetes Centre Core Lab at Mt Sinai Hospital. Impaired fasting glucose (IFG),
impaired glucose tolerance (IGT), and diabetes were categorized using the 2006
WHO criteria [@WHO2006].

TAGFA composition was quantified using stored fasting serum samples from the 
baseline visit, which had been frozen at -70°C for 4-6 years and had not been 
exposed to any freeze-thaw cycles. Serum fatty acids have been documented to be 
stable at these temperatures for up to 10 years [@Matthan2010a]. A known amount 
of triheptadecanoin (17:0; Nu-Chek Prep, Inc Elysian, MN, USA) was added as an internal
standard prior to extracting total lipids according to the method of Folch 
[@Folch1957a]. Each serum lipid fraction (non-esterified fatty acids (NEFA), 
cholesteryl ester, phospholipid, and TAG) was isolated using thin layer 
chromatography. Fatty acid methyl esters were separated and quantified using a 
Varian-430 gas chromatograph (Varian, Lake Forest, CA, USA) equipped with a 
Varian Factor Four capillary column and a flame ionization detector. Fatty acid 
concentrations (nmol/ml) were calculated by proportional comparison of gas
chromatography peak areas to that of the internal standards [@Nishi2014a]. There
were 22 fatty acids measured in the TAGFA fraction. 
Findings
for other lipid fractions in this cohort are reported separately (see ref
@Johnston2016a for the analysis of the phospholipid and cholesteryl ester
fractions). 
<!--and {{next citation}} for the analysis of the NEFA fraction).-->

@@

Insulin sensitivity and beta-cell function indices were computed using the OGTT 
glucose and insulin data. Insulin sensitivity was assessed using the Insulin
Sensitivity Index (ISI) [@Matsuda1999] and HOMA2-%S [@Levy1998a] using the HOMA2
Calculator. HOMA largely reflects hepatic insulin sensitivity, while ISI
reflects whole-body insulin sensitivity [@AbdulGhani2007]. Beta-cell function
was assessed using the Insulinogenic Index [@Wareham1995] over HOMA-IR [@Matthews1985] (IGI/IR)
and the Insulin Secretion-Sensitivity Index-2 (ISSI-2) [@Retnakaran2009]. IGI/IR
is a measure of the first phase of insulin secretion while ISSI-2 is analogous to
the disposition index (but is calculated using OGTT values). Each index has been validated
against gold standard measures [@Matthews1985; @Hermans1999a; @Matsuda1999; @Retnakaran2009].
Specific formulas for each OGTT-derived measure can be found in the 
Supplementary Material.

The primary outcome variables for this analysis were HOMA2-%S, ISI, IGI/IR, and
ISSI-2, which were log-transformed for the statistical modeling. The primary
predictor variables for this analysis were 22 individual TAGFA included as either mole percent
(mol%) of the total fraction or as a concentration (nmol/mL). Clinically-measured
TAG was also included as a primary predictor to allow us to test the hypothesis
that specific TAGFA better predicted outcomes compared to clinical TAG. 
Pearson correlation coefficients were computed to assess the relationships of
individual TAGFA with other continuous variables. Correlations were also
computed for TAGFA against each other; hierarchical clustering analysis was
applied to the correlation matrix to identify potential clusters within the TAGFA 
composition.

Generalized estimating equation (GEE) models [@Zeger1986a] were used in the 
primary analysis to determine the longitudinal associations between the outcome 
variables and the predictor variables. The predictor variables and continuous 
covariates were scaled (mean-centered and standardized). Given the longitudinal 
design, an auto-regressive of order 1 (AR1) working correlation matrix was 
specified in the GEE model. Covariates to adjust for were selected based on the
previous literature, from directed acyclic graph [@Greenland1999a]
recommendations, and from quasi-likelihood information criteria (QIC). The final
GEE model was adjusted for time, waist circumference, baseline age, ethnicity,
sex, ALT, MET, and total NEFA. The TAGFA, total NEFA, sex, ethnicity, and
baseline age were classified as *time-independent* (held constant) as they were
measured only at the baseline visit or do not change throughout the study, while
the outcome variables and remaining covariates were set as *time-dependent*.
After transformations, the GEE estimates are interpreted as an expected percent 
difference in the outcome variable for every standard deviation (SD) increase in
the predictor variable given the covariates are held constant (including time). 
We also tested for an interaction with sex, ethnicity, or time by the predictor 
term for each outcome variable. See the Supplemental Methods for an expanded 
explanation of the GEE modeling analysis.

@@

All analyses were performed using R `r getRversion()` [@Rbase], along with the R
packages geepack `r packageVersion('geepack')` for GEE [@Hoejsgaard2006a] and pls
`r packageVersion('pls')` for PLS. The R code and extra analyses for
this manuscript is available at {{code doi}}. Results were considered
statistically significance at p<0.05, after adjusting for multiple testing using
the Benjamini-Hochberg False Discovery Rate [@Benjamini1995a]. STROBE was used
as a guideline for reporting [@Vandenbroucke2007b].

@@

`r cite_t('basic')` shows basic characteristics of the PROMISE cohort. The mean 
follow-up time was `r calc_followup_time()` years, where `r calc_pct_full_visits()`%
of participants attended all three visits. There were
`r female$npct` females and `r euro$npct` who had European-ancestry, with a mean
age in years of `r aide::ave_sd(ds0yr$Age)` and a mean BMI
of `r aide::ave_sd(ds0yr$BMI)` kg/m^2^. As expected from the study's eligibility
criteria, the majority of participants, n=`r fhd$npct`, had a family history of
diabetes. Between the baseline visit and the 6-year visit in this sample,
insulin sensitivity and beta-cell function measures had a significant median decline of
between `r outcome_chg$chg` (p`r outcome_chg$p` from GEE; n=`r outcome_chg$n`). There 
were `r dys$pre` and `r dys$dm` incident cases of pre-diabetes (IFG and IGT) and
diabetes, respectively, over the 6-years; these observations were excluded from GEE and PLS
analyses.

`r cite_f('tagfa')` shows the composition of each FA in the TAG fraction (see 
`r cite_st('tagfa')` for a tabular presentation of the values). 
Three TAGFA contributed `r format_rounding(sum(tagfa$pct))`% to the total 
TAG concentration: `r tagfa$c[1]`; `r tagfa$c[2]`; and, `r tagfa$c[3]`.
`r cite_f('heatmap')` shows a heatmap of the correlation of individual TAGFA as
concentrations with the outcome variables and several basic characteristics.
As expected, nearly all TAGFA had very strong positive correlations (r=
`r fa_cor$rng$TAG[2]`) with clinically-measured TAG and moderate positive 
correlations with WC (r=`r fa_cor$rng$Waist[2]`). There was also moderate
negative correlations with HDL (r=`r fa_cor$rng$HDL[1]`). For the outcome variables,
the correlations for the insulin sensitivity measures were generally higher 
(HOMA2-%S: r=`r fa_cor$rng[['HOMA2-%S']][1]`, ISI: r=`r fa_cor$rng$ISI[1]`) than 
for the beta-cell function measures (all r<0.30). For correlations
of individual TAGFA using mol% with the basic participant characteristics, as shown in 
`r cite_f('heatmap_mol')`, differences in correlations between fatty acids were
most evident for 14:0, 14:1n-7, 16:0, and 16:1n-7 that had a moderate positive
correlation with clinical TAG (r=`r fa_cor_mol$rng$TAG[1]`) while all other fatty
acids had a negative association (r=`r fa_cor_mol$rng$TAG[2]`). In particular,
those fatty acids with the negative associations with clinical TAG were all the
very long chain polyunsaturated fatty acids (e.g. 20:4n-6, 20:5n-3).
Based on heirarchical cluster analysis of the inter-correlation matrix of the
TAGFA fraction, shown in `r cite_f('heatmap_tagfa')`, four fatty acids (14:0,
16:0, 14:1n-7, and 16:1n-7) displayed a marked separation and cluster from the
other TAGFA.

>>>>

**Research Design and Methods**:
We used longitudinal data (3 visits over 6 years) from the Prospective
Metabolism and Islet Cell Evaluation (PROMISE) cohort of adults (n=477) who were at-risk
for diabetes at baseline. Glucose and insulin from an OGTT were used to calculate the outcome variables
Matsuda index (ISI), HOMA2-%S, Insulinogenic Index over HOMA-IR (IGI/IR),
and Insulin Secretion-Sensitivity Index-2 (ISSI-2). Gas chromatography
quantified TAGFA composition. Generalized estimating equations (GEE) adjusted for
confounders and partial least squares (PLS) were used for the analysis.

@@

Hypertriglyceridemia is a well described metabolic disorder resulting in negative health outcomes [@Chehade2013a].
It is a risk factor for cardiovascular disease [@DAgostino2004a; @Verges2015a]
and is associated with other metabolic disorders such as non-alcoholic
fatty liver disease [@Kawano2013a], the metabolic syndrome [@Alberti2009], and
abdominal obesity [@Lemieux2000a].
Circulating triacylglceride (TAG) concentration is commonly measured during
routine clinical assessment using enzymatic methods.
However, clinically measured TAG is limited as it
represents the full fatty acid spectrum within the TAG fraction as a summary
measure. There is increasing appreciation for the importance of specific fatty 
acid composition profiles in different plasma fractions on various health
outcomes [@Forouhi2014a; @Ma2015a; @Johnston2016a], however there are relatively
few studies that have explored the impact of the fatty acid composition in the TAG fraction [@Rhee2011a; @Lankinen2015a].

The interaction between TAG and insulin sensitivity is complex and involves 
components of a feedback system [@Verges2015a]. Greater resistance to insulin in
both the liver and muscle may result in greater production of TAG and secretion
of lipoproteins that transport TAG [@Yu2012a]. Likewise, greater TAG may
contribute to metabolic dysfunction and lipotoxicity in various tissues,
affecting insulin sensitivity, and thus continue the cycle [@Verges2015a]. Given the
complexity and temporal nature of the relationship, long term studies with
multiple data collection time points are paramount to better understanding the underlying
biology and subsequent risk.

While several studies have documented prospective associations of 
hypertriglyceridemia with incident type 2 diabetes 
[@Chien2008a; @DAgostino2004a; @Schulze2009a], only a limited number of longitudinal
studies [@Rhee2011a; @Lankinen2015a] have examined the relationship between
TAG and its composition with the pathophysiological factors underlying diabetes, 
particularly beta-cell function. Our objective was to examine the 
longitudinal role of the specific composition of the serum TAG fraction on 
OGTT-derived measures of insulin sensitivity and beta-cell function compared to 
clinically measured TAG in a Canadian population at risk for diabetes.

@@

Recruitment for the baseline visit of the Prospective Metabolism and Islet Cell Evaluation (PROMISE) 
cohort took place between 2004-2006 in London and Toronto, 
Canada. Individuals were selected to participate if they met the eligibility 
criteria of having one or more risk factors for type 2 diabetes mellitus, 
including obesity, hypertension, family history of diabetes, and/or a history of
gestational diabetes or birth of a macrosomic infant. A total of 736 individuals
attended the baseline visit. Subsequent examinations occurred every three years,
with data from three examination visits available for the present analysis
(2004-2006, 2007-2009, and 2010-2013). The current study
used data on participants who did not have diabetes at baseline, who
returned for one or more of the follow-up examinations, and who had samples
available for fatty acid measurements (n=477; see the CONSORT diagram in 
`r cite_sf('consort')`). Metabolic characterization, anthropometric
measurements, and questionnaires on lifestyle and sociodemographics were
administered at each examination visit. Research ethics approval was obtained from
Mount Sinai Hospital and the University of Western Ontario, and all participants
provided written informed consent. Data collection methods were standardized
across the 2 centres and research nurses were centrally trained.

@@

After 8-12 hours of overnight fasting, participants completed a 75g oral glucose tolerance test (OGTT) at 
each examination visit, with blood samples taken at fasting, 30 min, and 2 hr 
post-glucose load. Samples were subsequently processed and frozen at -70°C.
Alanine aminotransferase (ALT) was measured using standard laboratory 
procedures. Cholesterol, HDL, and clinically-measured TAG 
were measured using Roche Modular's enzymatic colorimetric tests (Mississauga, 
ON). Both insulin and glucose were
measured from OGTT blood samples at fasting, 30 minute,
and 2 hour time points. Specific insulin was measured with the Elecsys 1010 
(Roche Diagnostics, Basel, Switzerland) immunoassay analyzer and 
electrochemiluminescence immunoassay, which shows 0.05% cross-reactivity to 
intact human pro-insulin and the Des 31,32 circulating split form (Linco Res. 
Inc) and has a coefficient of variation (CV) of 9.3%. Glucose was determined 
using an enzymatic hexokinase method (Roche Modular, Roche Diagnostics) with a 
detection range of 0.11 to 41.6 mmol/L and an inter-assay CV of <1.1% and an
intra-assay CV of < 1.9%.  All assays were performed at the Banting and Best
Diabetes Centre Core Lab at Mt Sinai Hospital. Impaired fasting glucose (IFG),
impaired glucose tolerance (IGT), and diabetes were categorized using the 2006
WHO criteria [@WHO2006].

TAGFA composition was quantified using stored fasting serum samples from the 
baseline visit, which had been frozen at -70°C for 4-6 years and had not been 
exposed to any freeze-thaw cycles. Serum fatty acids have been documented to be 
stable at these temperatures for up to 10 years [@Matthan2010a]. A known amount 
of triheptadecanoin (17:0; Nu-Chek Prep, Inc Elysian, MN, USA) was added as an internal
standard prior to extracting total lipids according to the method of Folch 
[@Folch1957a]. Each serum lipid fraction (non-esterified fatty acids (NEFA), 
cholesteryl ester, phospholipid, and TAG) was isolated using thin layer 
chromatography. Fatty acid methyl esters were separated and quantified using a 
Varian-430 gas chromatograph (Varian, Lake Forest, CA, USA) equipped with a 
Varian Factor Four capillary column and a flame ionization detector. Fatty acid 
concentrations (nmol/ml) were calculated by proportional comparison of gas
chromatography peak areas to that of the internal standards [@Nishi2014a]. There
were 22 fatty acids measured in the TAGFA fraction. 
Findings
for other lipid fractions in this cohort are reported separately (see ref
@Johnston2016a for the analysis of the phospholipid and cholesteryl ester
fractions). {{put these analyses in discussion?}}
<!--and {{next citation}} for the analysis of the NEFA fraction).-->

@@

Insulin sensitivity and beta-cell function indices were computed using the OGTT 
glucose and insulin data. Insulin sensitivity was assessed using the Insulin
Sensitivity Index (ISI) [@Matsuda1999] and HOMA2-%S [@Levy1998a] using the HOMA2
Calculator. HOMA largely reflects hepatic insulin sensitivity, while ISI
reflects whole-body insulin sensitivity [@AbdulGhani2007]. Beta-cell function
was assessed using the Insulinogenic Index [@Wareham1995] over HOMA-IR [@Matthews1985] (IGI/IR)
and the Insulin Secretion-Sensitivity Index-2 (ISSI-2) [@Retnakaran2009]. IGI/IR
is a measure of the early phase of insulin secretion while ISSI-2 is analogous to
the disposition index (but is calculated using OGTT values). Each index has been validated
against gold standard measures [@Matthews1985; @Hermans1999a; @Matsuda1999; @Retnakaran2009].
Specific formulas for each OGTT-derived measure can be found in the 
Supplemental Material {{insert formula}}.

The primary outcome variables for this analysis were HOMA2-%S, ISI, IGI/IR, and
ISSI-2, which were log-transformed for the statistical modeling. The primary
predictor variables for this analysis were 22 individual TAGFA included as either mole percent
(mol%) of the total fraction or as a concentration (nmol/mL). Clinically-measured
TAG was also included as a primary predictor to allow us to test the hypothesis
that specific TAGFA better predicted outcomes compared to clinical TAG. 
Pearson correlation coefficients were computed to assess the relationships of
individual TAGFA with other continuous variables. Correlations were also
computed for TAGFA against each other; hierarchical clustering analysis was
applied to the correlation matrix to identify clusters within the TAGFA 
composition. {{expand/clarify, ref suplemental material}}

Generalized estimating equation (GEE) models [@Zeger1986a] were used in the 
primary analysis to determine the longitudinal associations between the outcome 
variables and the predictor variables. The predictor variables and continuous 
covariates were scaled (mean-centered and standardized). Given the longitudinal 
design, an auto-regressive of order 1 (AR1) working correlation matrix was 
specified in the GEE model. Covariates to adjust for were selected based on the
previous literature, from directed acyclic graph [@Greenland1999a]
recommendations, and from quasi-likelihood information criteria (QIC). The final
GEE model ({{M#?}}) was adjusted for time, waist circumference, baseline age, ethnicity,
sex, ALT, MET, and total NEFA. The TAGFA, total NEFA, sex, ethnicity, and
baseline age were classified as *time-independent* (held constant) as they were
measured only at the baseline visit or do not change throughout the study, while
the outcome variables and remaining covariates were set as *time-dependent*.
After transformations, the GEE estimates are interpreted as an expected percent 
difference in the outcome variable for every standard deviation (SD) increase in
the predictor variable given the covariates are held constant (including time). 
We also tested for an interaction with sex, ethnicity, or time by the predictor 
term for each outcome variable. See the Supplemental Methods for an expanded 
explanation of the GEE modeling analysis.

@@

All analyses were performed using R `r getRversion()` [@Rbase], along with the R
packages geepack `r packageVersion('geepack')` for GEE [@Hoejsgaard2006a] and pls
`r packageVersion('pls')` for PLS. The R code and extra analyses for
this manuscript is available at {{code doi}}. Results were considered
statistically significant at p<0.05, after adjusting for multiple testing using
the Benjamini-Hochberg False Discovery Rate [@Benjamini1995a]. STROBE was used
as a guideline for reporting [@Vandenbroucke2007b].

@@

`r cite_t('basic')` shows basic characteristics of the PROMISE cohort. The mean 
follow-up time was `r calc_followup_time()` years, where `r calc_pct_full_visits()`%
of participants attended all three visits. There were
`r female$npct` females and `r euro$npct` who had European-ancestry, with a mean
age in years of `r aide::ave_sd(ds0yr$Age)` and a mean BMI
of `r aide::ave_sd(ds0yr$BMI)` kg/m^2^. As expected from the study's eligibility
criteria, the majority of participants, n=`r fhd$npct`, had a family history of
diabetes. Between the baseline visit and the 6-year visit in this sample,
insulin sensitivity and beta-cell function measures had a significant median decline of
between `r outcome_chg$chg` (p`r outcome_chg$p` from GEE; n=`r outcome_chg$n`). There 
were `r dys$pre` and `r dys$dm` incident cases of pre-diabetes (IFG and IGT) and
diabetes, respectively, over the 6-years; these observations were excluded from GEE and PLS
analyses due to how the outcomes were measured (OGTT was not done on those with diabetes).

`r cite_f('tagfa')` shows the composition of each FA in the TAG fraction (see 
`r cite_st('tagfa')` for a tabular presentation of the values). 
Three TAGFA contributed `r format_rounding(sum(tagfa$pct))`% to the total 
TAG concentration: `r tagfa$c[1]`; `r tagfa$c[2]`; and, `r tagfa$c[3]`.
`r cite_f('heatmap')` shows a heatmap of the correlation of individual TAGFA as
concentrations with the outcome variables and several basic characteristics.
As expected, nearly all TAGFA had very strong positive correlations (r=
`r fa_cor$rng$TAG[2]`) with clinically-measured TAG and moderate positive 
correlations with WC (r=`r fa_cor$rng$Waist[2]`). There were also moderate
negative correlations with HDL (r=`r fa_cor$rng$HDL[1]`). For the outcome variables,
the correlations for the insulin sensitivity measures were generally higher 
(HOMA2-%S: r=`r fa_cor$rng[['HOMA2-%S']][1]`, ISI: r=`r fa_cor$rng$ISI[1]`) than 
for the beta-cell function measures (all r<0.30). For correlations
of individual TAGFA using mol% with the basic participant characteristics, as shown in 
`r cite_f('heatmap_mol')`, differences in correlations between fatty acids were
most evident for 14:0, 14:1n-7, 16:0, and 16:1n-7 that had a moderate positive
correlation with clinical TAG (r=`r fa_cor_mol$rng$TAG[1]`) while all other fatty
acids had a negative association (r=`r fa_cor_mol$rng$TAG[2]`). In particular,
those fatty acids with the negative associations with clinical TAG were all the
very long chain polyunsaturated fatty acids (e.g. 20:4n-6, 20:5n-3).
Based on heirarchical cluster analysis of the inter-correlation matrix of the
TAGFA fraction, shown in `r cite_f('heatmap_tagfa')`, four fatty acids (14:0,
16:0, 14:1n-7, and 16:1n-7) displayed a marked separation and cluster from the
other TAGFA. {{clarify, as well as the legend}}
